Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-09 background/background.tex
Fix order

The feature that ABC algorithm can perform likelihood-free inference makes it widely used in many dynamic modeling problems, especially in the area of biology \cite{ref:abcsysbio, ref:compare, ref:disease}. But ABC is not limited to these areas, as it can be generally used in inference tasks to give parameter estimates or model rankings. E.g., it has been successfully applied in cosmology studies \cite{cosmology}.

>>>>

The feature that ABC algorithm can perform likelihood-free inference makes it widely used in many dynamic modeling problems, especially in the area of biology \cite{ref:abcsysbio, ref:disease, ref:compare}. But ABC is not limited to these areas, as it can be generally used in inference tasks to give parameter estimates or model rankings. E.g., it has been successfully applied in cosmology studies \cite{cosmology}.
